---
title: "Visual Exploration of Dairy Products in the United States" 
author: "Becca Furbeck, Kassidy Buse, Samantha Teten"
date: "11/21/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## The Set-Up {data-background=background.jpg data-background-size=cover}
<div class= "black">

Our team has been approached by a business person who happens to love dairy products! They are interested in starting a dairy to live out their childhood dreams, but are not sure where to start. We combed the USDA and FDA data to make recommendations to ensure they get the best dairy possible. 
</div>

## HOLY COW


There is a lot to consider! Maybe exploratory analysis can help!

```{r cows, echo = FALSE, warning=FALSE, message=FALSE}
library(magick)
library(magrittr)
library(purrr)

cowsgif<-list.files("Cow Pics PNG", pattern = '*.png', full.names = TRUE) %>% 
        image_read() %>% 
        image_join() %>% 
        image_scale("x300")%>%
        image_animate(fps=2) 

cowsgif
```

## Questions to Answer 

- Where is the best place in the United States to run a dairy operation?
- What products are the most profitable?
- What are hazards to look out for during production to avoid recalls?


## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```



## Where should we operate?

Kassidy introduces her dataset

## Kassidy Plot

hooray U.S.A.

## Kassidy recommendations

put your farm in a state where you can make money yo

## What Products should we make?

Sam introduces her dataset

## Sam Plot

## Sam Recommendations

make this product and make mad money yo

## What should the producer look out for?

Becca introduce dataset/scrape methods

## Worldcloud Plot

## Monthly Occurances - Major Outbreak Plot

## Becca Recommendations

Don't mess with *Listeria* yo


