---
title: "Stat 850 Project Description"
author: "Rebecca Furbeck, Firstname Lastname, Samantha Teten"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(digits = 3)
```

```{r load-sas-libraries, echo = F, message = F, warning = F}

saspath <- "/usr/local/SASHome/SASFoundation/9.4/bin/sas_en" # Your SAS path goes here
sasopts <- "-ls 75"
knitr::opts_chunk$set(engine.path=list(sas=saspath, saslog=saspath, sashtml=saspath),
                      engine.opts=list(sas=sasopts, saslog=sasopts, sashtml=sasopts), 
                      comment=NA)
library(SASmarkdown)
```

## Instructions

Each member of your team should modify this document in some way and push their modifications to the repository in a separate commit. This will ensure that you have set your repository up in a way that ensures all group members are working with the same repository. 

Note that you must compile your readme (this document) for it to properly display as part of your github repository. 

Once you have received feedback on your project proposal (via Canvas) you may alter this README so that it describes your final project instead of the project proposal. 

## Data Set
Provide a link to your dataset here, and a description of the variables in the data set.

See csv files

## Potential Topics to Explore Using the Data Set
Scenario: We are a team of agricultural scientists, who have been contacted by a business group interested in starting a dairy products creamery operation. They are looking to learn 

We intend to learn:
What in the world in happening in 2020 with milk prices? 
What location should we processed in? (Investigate which states are excelling in milk production to have a supply chain)
What products should we make? (Investigate the sales of products over time)
What difficulties could arise or things should we be aware of? (FDA Recalls)

## Group Members
Samantha Teten
Kassidy Buse
Becca Furbeck

## Stuff to look at
- map of change in milk prod for each state (US Map) from 1970 to 2014
-change in milk production from 1970 to 2014 for top 3 states
