---
title: "Stat 850 Project Description"
author: "Rebecca Furbeck, Kassidy Buse, Samantha Teten"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(digits = 3)
```

```{r load-sas-libraries, echo = F, message = F, warning = F}

saspath <- "/usr/local/SASHome/SASFoundation/9.4/bin/sas_en" # Your SAS path goes here
sasopts <- "-ls 75"
knitr::opts_chunk$set(engine.path=list(sas=saspath, saslog=saspath, sashtml=saspath),
                      engine.opts=list(sas=sasopts, saslog=sasopts, sashtml=sasopts), 
                      comment=NA)
library(SASmarkdown)
```


## Data Set
We are using 2 main entities for data.

The first portion is provided by the USDA ERS:
https://www.ers.usda.gov/data-products/dairy-data/
Variables in these datasets (see CSVs below) are mainly numeric, pertaining to production and sales of dairy products. 

The second being the FDA recalls and notices: https://www.fda.gov/safety/recalls-market-withdrawals-safety-alerts
Variables included in this data set are dates, and characters detailing food brand, product description, product type, and recall reason. 

See csv files in repository.
```{r}
library(readr)
library(tidyverse)
whole_milk_header <- read_csv("whole_milk.csv", n_max = 2) %>%
  mutate(across(everything(), ~ifelse(is.na(.), "", .))) %>%
  summarize(across(everything(), paste, collapse = "_")) %>%
  mutate(across(everything(), str_remove, "_$")) %>% 
  unlist() %>% as.character()
whole_milk <- read_csv("whole_milk.csv", 
                       col_names = whole_milk_header, 
                       col_types = "dddd_", skip = 3) %>%
  filter(Year <= 2018) %>%
  select(-5)

head(whole_milk)
NROW(whole_milk)

dairy_basket<-readLines("dairy_basket.csv")
head(dairy_basket)
NROW(dairy_basket)

butter<-readLines("butter.csv")
head(butter)
NROW(butter)

cheese<-readLines("cheese.csv")
head(cheese)
NROW(cheese)

ice_cream<-readLines("ice_cream.csv")
head(ice_cream)
NROW(ice_cream)
```

## Potential Topics to Explore Using the Data Set
Scenario: We are a team of agricultural scientists who have been contacted by a business group interested in starting a dairy products creamery operation. They are looking to learn 

We intend to learn:
What in the world in happening in 2020 with milk prices? 
What location should we processed in? (Investigate which states are excelling in milk production to have a supply chain)
What products should we make? (Investigate the sales of products over time)
What difficulties could arise or things should we be aware of? (FDA Recalls)

## Group Members
Samantha Teten
Kassidy Buse
Becca Furbeck

## Stuff to look at
- map of change in milk prod for each state (US Map) from 1970 to 2014
-change in milk production from 1970 to 2014 for top 3 states
-spread of farm price from retail price over time
-Reasons for recalls of dairy products
