---
title: "Stat 850 Project Description"
author: "Firstname Lastname, Firstname Lastname, Samantha Teten"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(digits = 3)
```

```{r load-sas-libraries, echo = F, message = F, warning = F}

saspath <- "/usr/local/SASHome/SASFoundation/9.4/bin/sas_en" # Your SAS path goes here
sasopts <- "-ls 75"
knitr::opts_chunk$set(engine.path=list(sas=saspath, saslog=saspath, sashtml=saspath),
                      engine.opts=list(sas=sasopts, saslog=sasopts, sashtml=sasopts), 
                      comment=NA)
library(SASmarkdown)
```

## Instructions

Each member of your team should modify this document in some way and push their modifications to the repository in a separate commit. This will ensure that you have set your repository up in a way that ensures all group members are working with the same repository. 

Note that you must compile your readme (this document) for it to properly display as part of your github repository. 

Once you have received feedback on your project proposal (via Canvas) you may alter this README so that it describes your final project instead of the project proposal. 

## Data Set
Provide a link to your dataset here, and a description of the variables in the data set.

https://github.com/rfordatascience/tidytuesday/blob/master/data/2019/2019-01-29/fluid_milk_sales.csv

https://github.com/rfordatascience/tidytuesday/blob/master/data/2019/2019-01-29/milkcow_facts.csv


```{r, readdata}
stateprod <- read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-01-29/state_milk_production.csv")
write.csv(stateprod, "stateprod.csv")

products <- read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-01-29/milk_products_facts.csv")
write.csv(products, "products.csv")



```

## Potential Topics to Explore Using the Data Set
Describe avenues you might explore using the data

## Group Members
Samantha Teten
Kassidy Buse
Becca Furbeck
