---
title: "USMap"
author: "Kassidy Buse"
date: "11/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, we need to pull in the data set that includes the milk production for each state and region
```{r}
urlfile <- "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-01-29/state_milk_production.csv"
dairycsv <- read.csv(urlfile)
dairybystate <- as.data.frame(dairycsv)
```

explore a little
```{r}
range(dairybystate$milk_produced)
```

Smallest value is     3,000,000
Largest value is 42,339,000,000
Yikes that is a large range. 
```{r}
which.min(dairybystate$milk_produced)
which.max(dairybystate$milk_produced)
```

Wonder who they are (let's be honest...the low is either AK or HI)
```{r}
dairybystate[2199,]
```
Like I said, AK or HI. I'm betting the high is CA...because happy cows are in CA...or just very hot ones
```{r}
dairybystate[2248,]
```

Of course it is CA...and 2014 was a great year for dairy so that isn't surprising at all.

I obviously can't plot every year, and with a range this large, the continuous fill scale would be so broad that it wouldn't accurately depict the data. So, we have to break this down. 

Filtering the data down to some "key" years for map making. 
```{r}
library(tidyverse)
dairy70 <- dairybystate %>% filter(year == 1970)
dairy80 <- dairybystate %>% filter(year == 1980)
dairy90 <- dairybystate %>% filter(year == 1990)
dairy00 <- dairybystate %>% filter(year == 2000)
dairy10 <- dairybystate %>% filter(year == 2010)
dairy17 <- dairybystate %>% filter(year == 2017)
```

Now to find the ranges of these years. 
```{r}
range(dairy70$milk_produced)
```
```{r}
range(dairy80$milk_produced)
```

```{r}
range(dairy90$milk_produced)
```

```{r}
range(dairy00$milk_produced)
```

```{r}
range(dairy10$milk_produced)
```

```{r}
range(dairy17$milk_produced)
```

So it looks like our minimum value is 3,000,000 and our maximum value is 40,385,000,000. 
Well, that didn't help much, but logically, we can eliminate the lower bounds because we aren't interested in these small states with limited supply, we want the milk. 

## Where Kassidy's eyes were bigger than her plate: 

### Making a freaking cool map

1970
```{r}
library(usmap)
library(ggplot2)

usa70 <- plot_usmap(regions = "states", data = dairy70, values = "milk_produced", color = "black") + 
  scale_fill_continuous(low = "purple", high = "orange", name = "Production, lb", label = scales::comma, breaks = c(10000000000, 20000000000, 30000000000, 40000000000), limits = c(2500000000, 45000000000)) +
  labs(title = "Dairy Production in the United States",
       subtitle = "Changes in dairy produciton by state in 1970") + 
  theme(panel.background = element_rect(color = "black", fill = "white"), legend.position = "right")

ggsave(filename = "usa70.png", plot=usa70,width=4,height=4,units="in",scale=1)
usa70pic <- image_read("usa70.png")
```

1980
```{r}
library(usmap)
library(ggplot2)

usa80 <- plot_usmap(regions = "states", data = dairy80, values = "milk_produced", color = "black") + 
  scale_fill_continuous(low = "purple", high = "orange", name = "Production, lb", label = scales::comma, breaks = c(10000000000, 20000000000, 30000000000, 40000000000), limits = c(2500000000, 45000000000)) +
  labs(title = "Dairy Production in the United States",
       subtitle = "Changes in dairy produciton by state in 1980") + 
  theme(panel.background = element_rect(color = "black", fill = "white"), legend.position = "right")

ggsave(filename = "usa80.png", plot=usa80,width=4,height=4,units="in",scale=1)
usa80pic <- image_read("usa80.png")
```

1990
```{r}
library(usmap)
library(ggplot2)

usa90 <- plot_usmap(regions = "states", data = dairy90, values = "milk_produced", color = "black") + 
  scale_fill_continuous(low = "purple", high = "orange", name = "Production, lb", label = scales::comma, breaks = c(10000000000, 20000000000, 30000000000, 40000000000), limits = c(2500000000, 45000000000)) +
  labs(title = "Dairy Production in the United States",
       subtitle = "Changes in dairy produciton by state in 1990") + 
  theme(panel.background = element_rect(color = "black", fill = "white"), legend.position = "right")

ggsave(filename = "usa90.png", plot=usa90,width=4,height=4,units="in",scale=1)
usa90pic <- image_read("usa90.png")
```

2000
```{r}
library(usmap)
library(ggplot2)

usa00 <- plot_usmap(regions = "states", data = dairy00, values = "milk_produced", color = "black") + 
  scale_fill_continuous(low = "purple", high = "orange", name = "Production, lb", label = scales::comma, breaks = c(10000000000, 20000000000, 30000000000, 40000000000), limits = c(2500000000, 45000000000)) +
  labs(title = "Dairy Production in the United States",
       subtitle = "Changes in dairy produciton by state in 2000") + 
  theme(panel.background = element_rect(color = "black", fill = "white"), legend.position = "right")

ggsave(filename = "usa00.png", plot=usa00,width=4,height=4,units="in",scale=1)
usa00pic <- image_read("usa00.png")
```

2010
```{r}
library(usmap)
library(ggplot2)

usa10 <- plot_usmap(regions = "states", data = dairy10, values = "milk_produced", color = "black") + 
  scale_fill_continuous(low = "purple", high = "orange", name = "Production, lb", label = scales::comma, breaks = c(10000000000, 20000000000, 30000000000, 40000000000), limits = c(2500000000, 45000000000)) +
  labs(title = "Dairy Production in the United States",
       subtitle = "Changes in dairy produciton by state in 2010") + 
  theme(panel.background = element_rect(color = "black", fill = "white"), legend.position = "right")

ggsave(filename = "usa10.png", plot=usa10,width=4,height=4,units="in",scale=1)
usa10pic <- image_read("usa10.png")
```

2017
```{r}
library(usmap)
library(ggplot2)

usa17 <- plot_usmap(regions = "states", data = dairy70, values = "milk_produced", color = "black") + 
  scale_fill_continuous(low = "purple", high = "orange", name = "Production, lb", label = scales::comma, breaks = c(10000000000, 20000000000, 30000000000, 40000000000), limits = c(2500000000, 40000000000)) +
  labs(title = "Dairy Production in the United States",
       subtitle = "Changes in dairy produciton by state in 2017") + 
  theme(panel.background = element_rect(color = "black", fill = "white"), legend.position = "right")

ggsave(filename = "usa17.png", plot=usa17,width=4,height=4,units="in",scale=1)
usa17pic <- image_read("usa17.png")
```

let's try and animate this...because that would just be cool

Here we have the whole data set...no select years like above(which are for the purpose of the report since you can't really animate a report)

```{r}
image <- c(usa70pic, usa80pic, usa90pic, usa00pic, usa10pic, usa17pic)

image_append(image_scale(image, "x200"))
```

AND WE MAKE A FREAKING COOL MAP!
```{r}

animatedmap <- image_animate(image_scale(image, "400x400"), fps = 1, dispose = "previous")
dairygif <- image_write(animatedmap, "usadairy.gif")

animatedmap
```

Now to look at the big 3 in a more *intense* fashion
```{r}
library(ggplot2)
library(gganimate)
library(hrbrthemes)

dairytotal <- dairybystate %>% 
  filter(state %in% c("California", "Wisconsin", "New York"))

d = dairytotal %>% 
  ggplot(aes(x = year, y = milk_produced, group = state, color = state)) +
  geom_line() +
  geom_point() +
  scale_color_manual(values = c("purple", "magenta", "orange")) +
  ggtitle("Milk production from 1970 to 2017 of the top 3 producing states") +
  theme_ipsum() +
  ylab("Milk Produced") +
  transition_reveal(year)

anim_save("top3dairy.gif")
```

```{r}
d
```
